### 2021-03-24 exploratory/2021/test_criteria.Rmd
Describe criteria options

>>>>

My interpretation of the criteria parameter options:

- `fit` = "query only mcc" - Move query sequence `X` to OTU `Y` if it improves the mcc calculated using **only the query seqs**.
- `combo` = "query & ref mcc" - Move query sequence `X` to OTU `Y` if it improves the mcc calculated using **the query & reference seqs**.
- `both` = "either" - Move query sequence `X` to OTU `Y` if **either** the `fit` mcc ("query only") or the `combo` mcc ("query & ref") score improves.
